An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-21 EconGrowth-R-Functions.Rnw
Now using nice macros for major and minor separator slides in the presentation. Also added a graph for the statistical parameters of the Sf models.

#############################
# Creates a graph with confidene intervals for the single-factor model for the given factor
##
createSFParamsGraph <- function(factor){
  # Figure out the exponent for the desired factor
  if (factor == "K"){
    exponentParameter <- "$\\alpha$"
  } else if (factor == "L"){
    exponentParameter <- "$\\beta$"
  } else if ((factor == "Q") || (factor == "X") || (factor == "U")){
    exponentParameter <- "$\\gamma$"
  }
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda or m), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable,
                   centers = value, #identifies where the dots should be placed
                   draw.bands = FALSE, #provides nicer error bars
                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
                   layout = c(2,1), #2 column, 1 row
                   col = "black", #Sets line color to black
                   lwd = 1, #Sets line width to 1.0
                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", exponentParameter)),
                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
                   scales = list(cex=scaleTextSize, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
                                 y=list(relation="free", #allow each axis to be different
                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
                                                c(0.0, 0.5, 1.0)
                                                )
                                        )
                                 )
                   )

>>>>

#############################
# Creates a graph with confidene intervals for the single-factor model for the given factor
##
createSFParamsGraph <- function(factor){
  # Figure out the exponent for the desired factor
  if (factor == "K"){
    exponentParameter <- "$\\alpha$"
  } else if (factor == "L"){
    exponentParameter <- "$\\beta$"
  } else if ((factor == "Q") || (factor == "X") || (factor == "U")){
    exponentParameter <- "$\\gamma$"
  }
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda or m), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable,
                   centers = value, #identifies where the dots should be placed
                   draw.bands = FALSE, #provides nicer error bars
                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
                   layout = c(2,1), #2 column, 1 row
                   col = "black", #Sets line color to black
                   lwd = 1, #Sets line width to 1.0
                   strip = strip.custom(bg="transparent", factor.levels=c("$\\lambda$", exponentParameter)),
                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
                   scales = list(cex=scaleTextSize, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
                                 y=list(relation="free", #allow each axis to be different
                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
                                                c(0.0, 0.5, 1.0)
                                                )
                                        )
                                 )
                   )

### 2013-03-21 EconGrowthSeminar.Rnw
Now using nice macros for major and minor separator slides in the presentation. Also added a graph for the statistical parameters of the Sf models.

@@

\begin{frame} %----------------------------
  \begin{center} \huge
    INTRODUCTION
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \Large
    Factors of Production
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \Large
    Economic Growth Models
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \Large
    The Question
  \normalsize \end{center}
  Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \huge
    DATA SOURCES
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \Large
    Economic Data
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \Large
    Energy Data
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \Large
    Historical Data
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \huge
    EVALUATION OF
    \vspace{\baselineskip}
    GROWTH MODELS
  \normalsize \end{center}
\end{frame}

@@

\begin{frame}{Curve-fitting As Optimization} %----------------------------
  \begin{itemize}
    \item{Select values of parameters to minimize errors ($SSE$) between predicted and historical economic output $y$}
    \vspace{\baselineskip}

    \item{Example: Single-factor Model with $q$}
    \begin{itemize}
      \item{$y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$}
      \item{Select $\lambda$ and $\gamma$ to minimize\\
            $SSE = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{$SSE$ Minimization}{US Single-factor with $q$} %---------------------------- 
<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
sf3DSSEGraph("US", "Q")
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}  
\end{frame}

@@

@@

@@

\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("US", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("UK", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{uk}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("JP", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{jp}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("CN", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{cn}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("ZA", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{za}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("SA", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{sa}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("IR", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ir}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("TZ", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{tz}{0.07}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("ZM", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{zm}{0.055}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdUS["CD", "lambda"]} & \Sexpr{cdUS["CD", "alpha"]} & \Sexpr{cdUS["CD", "beta"]} & \Sexpr{cdUS["CD", "gamma"]}\\
            \hline
            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdxUS["CD", "beta"]} & \Sexpr{cdxUS["CD", "gamma"]}\\
            \hline
            $u$   & \Sexpr{cduUS["CD", "lambda"]} & \Sexpr{cduUS["CD", "alpha"]} & \Sexpr{cduUS["CD", "beta"]} & \Sexpr{cduUS["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdJP["CD", "lambda"]} & \Sexpr{cdJP["CD", "alpha"]} & \Sexpr{cdJP["CD", "beta"]} & \Sexpr{cdJP["CD", "gamma"]}\\
            \hline
            $q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdxJP["CD", "beta"]} & \Sexpr{cdxJP["CD", "gamma"]}\\
            \hline
            $u$   & \Sexpr{cduJP["CD", "lambda"]} & \Sexpr{cduJP["CD", "alpha"]} & \Sexpr{cduJP["CD", "beta"]} & \Sexpr{cduJP["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_JP_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{jp}{0.055}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
            \hline
            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{za}{0.055}
\end{frame}

@@

@@

\begin{frame} %----------------------------
  \begin{center} \huge
    RESULTS
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \huge
    SUMMARY
  \normalsize \end{center}
\end{frame}

@@

\begin{frame} %----------------------------
  \begin{center} \huge
    APPENDIX
  \normalsize \end{center}
\end{frame}

>>>>

% Creates a major separator frame with specified text in ALL CAPS.
\newcommand{\majorSeparator}[1]{
\begin{frame} %----------------------------
  \begin{center} \huge
    \MakeUppercase{#1}
  \normalsize \end{center}
\end{frame}
}

% Creates a minor separator frame with specified text.
\newcommand{\minorSeparator}[1]{
\begin{frame} %----------------------------
  \begin{center} \Large
    #1
  \normalsize \end{center}
\end{frame}
}

@@

\majorSeparator{Introduction} %----------------------------

@@

\minorSeparator{Factors of Production} %----------------------------

@@

\minorSeparator{Economic Growth Models} %----------------------------

@@

\minorSeparator{The Question\\ \normalsize     
\vspace{\baselineskip} 
Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?} %----------------------------

@@

\majorSeparator{Data Sources}

@@

\minorSeparator{Economic Data}

@@

\minorSeparator{Energy Data}

@@

\minorSeparator{Historical Data}

@@

\majorSeparator{Evaluation of \vspace{\baselineskip} Growth Models}

\minorSeparator{Single-factor Models}

@@

\begin{frame}{Curve-fitting as Optimization} %----------------------------
  \begin{itemize}
    \item{Select values of parameters to minimize errors ($SSE$) between predicted and historical economic output ($y$)}
    \vspace{\baselineskip}

    \item{Example: Single-factor Model with $Q$}
    \begin{itemize}
      \item{$y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$}
      \item{Select $\lambda$ and $\gamma$ to minimize\\
            $SSE = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{$SSE$ Minimization}{US Single-factor with $Q$} %---------------------------- 
<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
sf3DSSEGraph("US", "Q")
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}  
\end{frame}

@@

\begin{frame}{Statistical Properties}{US Single-factor ($Q$)} %----------------------------
<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
createSFParamsGraph("Q")
@  
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}
\end{frame}

\minorSeparator{Cobb-Douglas (without Energy)}

@@

\minorSeparator{Cobb-Douglas (with Energy)}

@@

\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("US", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("UK", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{uk}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("JP", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{jp}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("CN", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{cn}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("ZA", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{za}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("SA", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{sa}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("IR", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ir}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("TZ", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{tz}{0.07}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $Q$} %----------------------------
<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("ZM", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{zm}{0.055}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdUS["CD", "lambda"]} & \Sexpr{cdUS["CD", "alpha"]} & \Sexpr{cdUS["CD", "beta"]} & \Sexpr{cdUS["CD", "gamma"]}\\
            \hline
            $Q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdxUS["CD", "beta"]} & \Sexpr{cdxUS["CD", "gamma"]}\\
            \hline
            $u$   & \Sexpr{cduUS["CD", "lambda"]} & \Sexpr{cduUS["CD", "alpha"]} & \Sexpr{cduUS["CD", "beta"]} & \Sexpr{cduUS["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{us}{0.055}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdJP["CD", "lambda"]} & \Sexpr{cdJP["CD", "alpha"]} & \Sexpr{cdJP["CD", "beta"]} & \Sexpr{cdJP["CD", "gamma"]}\\
            \hline
            $Q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdxJP["CD", "beta"]} & \Sexpr{cdxJP["CD", "gamma"]}\\
            \hline
            $u$   & \Sexpr{cduJP["CD", "lambda"]} & \Sexpr{cduJP["CD", "alpha"]} & \Sexpr{cduJP["CD", "beta"]} & \Sexpr{cduJP["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_JP_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{jp}{0.055}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
            \hline
            $Q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{za}{0.055}
\end{frame}

\minorSeparator{Constant Elasticity of Substituion (CES)}

@@

\minorSeparator{LINEX}

@@

\majorSeparator{Results}

@@

\majorSeparator{Summary}

@@

\majorSeparator{Appendix}
